---
title: "N741 Homework 1"
author: "Rosemary"
date: "1/31/2018"
output:
  html_document: default
  pdf_document: default
---
```{r}
library(gapminder)
library(ggplot2)
```

#Homework 01 Exercise- Task 1
Standard deviation for life expectancy
```{r}
round(sd(gapminder$lifeExp), digits=2)
```

Median for life expectancy
```{r}
round(median(gapminder$lifeExp), digits=2)
```

Sample size for life expectancy
```{r}
round(length(gapminder$lifeExp), digits=2)
```

#Homework 01 Exercise- Task 2
Mean for life expectancy by continent
```{r}
aggregate(lifeExp ~ continent, gapminder, mean)
```

Standard deviation for life expectancy by continent
```{r}
aggregate(lifeExp ~ continent, gapminder, sd)
```

#Homework 01 Exercise- Task 3
GG Plot GDperCap by Continent
```{r}
ggplot(gapminder, aes(x = continent, y = gdpPercap)) +
  geom_boxplot(outlier.colour = "hotpink") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4)
```

GG Plot Pop by Continent
```{r}
ggplot(gapminder, aes(x = continent, y = pop)) +
  geom_boxplot(outlier.colour = "hotpink") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1/4)
```

#Homework 01 Exercise- Task 4
Bubble plot for Americas and Asia for the year 1992

```{r}
gap_with_colors <-
  data.frame(gapminder,
             cc = I(country_colors[match(gapminder$country,
                                         names(country_colors))]))

keepers <- with(gap_with_colors,
                continent %in% c("Americas", "Asia") & year == 1992)
plot(lifeExp ~ gdpPercap, gap_with_colors,
     subset = keepers, log = "x", pch = 21,
     cex = sqrt(gap_with_colors$pop[keepers]/pi)/1500,
     bg = gap_with_colors$cc[keepers])
```

#Homework 01 Exercise - Task 5
The link for this exercise is located at
[https://github.com/RosemaryKinuthia/N741Homework1](https://github.com/RosemaryKinuthia/N741Homework1).




